Transforming Trash as an Artistic Act

### 2016-01-08 appendix_materials.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d
Appendix
Former-commit-id: f50b1827cfcdd3397352f16ee911421b2a0086a8

\appendix
\chapter{Examples of collected materials}

>>>>

\chapter{COLLECTED MATERIALS AND MAKING OF}

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
  \caption{Collected materials all together}
  \label{fig:CollectedAllTogether}
\end{figure}

% BugerKing - Starbucks
\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_burgerking.jpg}
    \caption{Burger King Bag}
    \label{fig:BurgerKingBag}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_starbucks.jpg}
    \caption{Starbucks Bag}
    \label{fig:StarbucksBag}
  \end{minipage}
\end{figure}

% Coffee Packages - Liva Bag
\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_coffee_packages.jpg}
    \caption{Coffee Packages}
    \label{fig:CoffeePackages}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_liva.jpg}
    \caption{Paper Bag}
    \label{fig:LivaBag}
  \end{minipage}
\end{figure}

% Envolpe - Bank Slips
\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_envelope.jpg}
    \caption{Envelope}
    \label{fig:Envelope}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_bankslips.jpg}
    \caption{Bank Slips}
    \label{fig:BankSlips}
  \end{minipage}
\end{figure}

% Varuna Gezgin - Cardboard
\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_cardboard.jpg}
    \caption{Cardboard}
    \label{fig:CardBoard}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_varuna_gezgin.jpg}
    \caption{Menu Pages}
    \label{fig:VarunaGezgin}
  \end{minipage}
\end{figure}

% Waste bin - Modshifters
\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_from.jpg}
    \caption{Waste Bin}
    \label{fig:CardBoard}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/collected_modshifters.jpg}
    \caption{Modshifters}
    \label{fig:Modshifters}
  \end{minipage}
\end{figure}
